FDT\thanks{Supported by organization x.}

### 2018-11-13 IPCO format/FDT.tex
bib fixed

\begin{document}
%
\title{FDT\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Robert Carr\inst{1}\orcidID{} \and
Arash Haddadan\inst{2}\orcidID{} \and
Cynthia Phillips\inst{3}\orcidID{}}
%
\authorrunning{Carr et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{University of New Mexico, Albuquerque NM 87131, USA\\
\email{bobcarr@unm.}\\   \and
Carnegie Mellon University, Pittsburgh, PA 15213, USA\\
\email{ahaddada@cmu.edu}\and
Sandia National Laboratories, Albuquerque, NM 87185, USA\\
\email{caphill@sandia.gov}}
%
\maketitle              % typeset the header of the con	tribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
150--250 words.

@@

Many researchers (see \cite{sw, vazirani}) have developed polynomial time algorithms that find solutions for special classes of MILPs whose cost are provably smaller than $C\cdot z_{LP}(I,c)$ for some $C$ which can be a constant number or dependent on some parameter of the MILP, e.g. $O(\log(n))$. However, for many combinatorial optimization problems there is a limit to such techniques. Let $g_I= \max_{c\geq 0}\frac{z_{IP}(I,c)}{z_{LP}(I,c)}$. Parameter $g_I$ depends on set $S(I)$ and the linear constraints in (\ref{S}) and is known as the \textit{integrality gap} of the formulation for instance $I$. It is easy to see, that we cannot hope to find solutions for the MILP with objective values better than $g_I\cdot z_{LP}(I,c)$. More generally we can define the integrality gap for a class of instances $\mathcal{I}$. In this case, the integrality gap for problem $\mathcal{I}$ is
\begin{equation}
g_\mathcal{I} = \max_{c\geq 0 , I\in\mathcal{I}}\frac{z_{IP}(I,c)}{z_{LP}(I,c)}
\end{equation}

@@

In contrast to Fact \ref{cara} which implies exact algorithms for problems with a gap of 1, Theorem \ref{CV} does not imply an approximation algorithm, since it does not suggest how to find such a convex combination in polynomial time. This points to an interesting open question.

@@

\subsection{Notation and Preliminaries}

@@

The FDT algorithm for 2EC iteratively applies Lemmas \ref{LPC2EC} and \ref{2ecpruning} to variables $x_1,\ldots,x_t$ to obtain leaf point solutions $L_t$. Then, we just need to apply Lemma \ref{rounddown} to obtain the 2-edge-connected multigraphs from every solution in $L_t$. Notice that $t\leq 2|V|-3$ \cite{}. By Lemma \ref{2ecpruning} we have
\begin{align*}
	\sum_{(x,\lambda)\in L_t} \frac{\lambda}{\sum_{(x,\lambda)\in L_t}\lambda} \floor{x} \leq \frac{1}{\sum_{(x,\lambda)\in L_t}\lambda} \sum_{(x,\lambda)\in L_t} \lambda {x} \leq g^t_{\EC} x^*.
\end{align*}

@@

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}

	\bibitem[CR98]{carr-ravi}
	Robert Carr and R.~Ravi.
	\newblock A new bound for the 2-edge connected subgraph problem.
	\newblock In {\em Proceedings of the 6th International IPCO Conference on
		Integer Programming and Combinatorial Optimization}, pages 112--125, London,
	UK, UK, 1998. Springer-Verlag.

	\bibitem[CV04]{CV}
	Robert Carr and Santosh Vempala.
	\newblock On the held-karp relaxation for the asymmetric and symmetric
	traveling salesman problems.
	\newblock {\em Mathematical Programming}, 100(3):569--587, Jul 2004.

	\bibitem[FGL05]{fp1}
	Matteo Fischetti, Fred Glover, and Andrea Lodi.
	\newblock The feasibility pump.
	\newblock {\em Mathematical Programming}, 104(1):91--104, Sep 2005.

	\bibitem[FS09]{fp2}
	Matteo Fischetti and Domenico Salvagnin.
	\newblock Feasibility pump 2.0.
	\newblock {\em Mathematical Programming Computation}, 1(2):201--222, Oct 2009.

	\bibitem[GJ79]{GJ79}
	M.R. Garey and D.S. Johnson.
	\newblock {\em Computers and Intractability -- A Guide to the Theory of
		{NP}-Completeness}.
	\newblock Freeman, San Francisco, CA, 1979.

	\bibitem[GLS93]{cons-cara}
	Martin Gr{\"o}tschel, L{\'a}szl{\'o} Lov{\'a}sz, and Alexander Schrijver.
	\newblock {\em Geometric Algorithms and Combinatorial Optimization}, volume~2.
	\newblock Second corrected edition edition, 1993.

	\bibitem[Jai98]{jain}
	Kamal Jain.
	\newblock A factor 2 approximation algorithm for the generalized steiner
	network problem.
	\newblock In {\em Proceedings of the 39th Annual Symposium on Foundations of
		Computer Science}, FOCS '98, pages 448--, Washington, DC, USA, 1998. IEEE
	Computer Society.

	\bibitem[RT87]{randomizedrounding}
	Prabhakar Raghavan and Clark~D. Tompson.
	\newblock Randomized rounding: A technique for provably good algorithms and
	algorithmic proofs.
	\newblock {\em Combinatorica}, 7(4):365--374, Dec 1987.

	\bibitem[Sch03]{schrijver}
	A.~Schrijver.
	\newblock {\em Combinatorial Optimization - Polyhedra and Efficiency}.
	\newblock Springer, 2003.

	\bibitem[Vaz01]{vazirani}
	Vijay~V. Vazirani.
	\newblock {\em Approximation Algorithms}.
	\newblock Springer-Verlag, Berlin, Heidelberg, 2001.

	\bibitem[Wol80]{Wolsey1980}
	Laurence~A. Wolsey.
	\newblock {\em Heuristic analysis, linear programming and branch and bound},
	pages 121--134.
	\newblock Springer Berlin Heidelberg, Berlin, Heidelberg, 1980.

	\bibitem[WS11]{sw}
	David~P. Williamson and David~B. Shmoys.
	\newblock {\em The Design of Approximation Algorithms}.
	\newblock Cambridge University Press, New York, NY, USA, 1st edition, 2011.

>>>>

\begin{document}
%
\title{FDT\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Robert Carr\inst{1}\orcidID{} \and
Arash Haddadan\inst{2}\orcidID{} \and
Cynthia Phillips\inst{3}\orcidID{}}
%
\authorrunning{R. Carr, A. Haddadan, C. Phillips}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{University of New Mexico, Albuquerque NM 87131, USA\\
\email{bobcarr@unm.}\\   \and
Carnegie Mellon University, Pittsburgh, PA 15213, USA\\
\email{ahaddada@cmu.edu}\and
Sandia National Laboratories, Albuquerque, NM 87185, USA\\
\email{caphill@sandia.gov}}
%
\maketitle              % typeset the header of the con	tribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
150--250 words.

@@

Many researchers (see \cite{vazirani,sw}) have developed polynomial time algorithms that find solutions for special classes of MILPs whose cost are provably smaller than $C\cdot z_{LP}(I,c)$ for some $C$ which can be a constant number or dependent on some parameter of the MILP, e.g. $O(\log(n))$. However, for many combinatorial optimization problems there is a limit to such techniques. Let $g_I= \max_{c\geq 0}\frac{z_{IP}(I,c)}{z_{LP}(I,c)}$. Parameter $g_I$ depends on set $S(I)$ and the linear constraints in (\ref{S}) and is known as the \textit{integrality gap} of the formulation for instance $I$. It is easy to see, that we cannot hope to find solutions for the MILP with objective values better than $g_I\cdot z_{LP}(I,c)$. More generally we can define the integrality gap for a class of instances $\mathcal{I}$. In this case, the integrality gap for problem $\mathcal{I}$ is
\begin{equation}
g_\mathcal{I} = \max_{c\geq 0 , I\in\mathcal{I}}\frac{z_{IP}(I,c)}{z_{LP}(I,c)}
\end{equation}

@@

In contrast to Proposition \ref{cara} which implies exact algorithms for problems with a gap of 1, Theorem \ref{CV} does not imply an approximation algorithm, since it does not suggest how to find such a convex combination in polynomial time. This points to an interesting open question.

@@

\subsection{Notation}
For vectors $x,y\in \bbbr_{n}$ we say $x$ dominates $y$ if $x_i\geq y_i$ for $i= 1,\ldots,n$. For $m\times n$ matrix $A$, let $A_j$ be the $j$-th row of $A$ and $A^j$ be the $j$-th column of $A$. Let $\textbf{1}$ be the vector of all ones of a suitable dimension. For a set $S$ of vectors in $\bbbr_{n}$, $\conv(S)$ is the convex hull of all the points in $S$.

@@

The FDT algorithm for 2EC iteratively applies Lemmas \ref{LPC2EC} and \ref{2ecpruning} to variables $x_1,\ldots,x_t$ to obtain leaf point solutions $L_t$. Then, we just need to apply Lemma \ref{rounddown} to obtain the 2-edge-connected multigraphs from every solution in $L_t$. Notice that since $x$ is an extreme point we have $t\leq 2|V|-3$ \cite{}. By Lemma \ref{2ecpruning} we have
\begin{align*}
	\sum_{(x,\lambda)\in L_t} \frac{\lambda}{\sum_{(x,\lambda)\in L_t}\lambda} \floor{x} \leq \frac{1}{\sum_{(x,\lambda)\in L_t}\lambda} \sum_{(x,\lambda)\in L_t} \lambda {x} \leq g^t_{\EC} x^*.
\end{align*}

@@

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{10}

		\bibitem{carr-ravi}
		Robert Carr and R.~Ravi.
		\newblock A new bound for the 2-edge connected subgraph problem.
		\newblock In {\em Proceedings of the 6th International IPCO Conference on
			Integer Programming and Combinatorial Optimization}, pages 112--125, London,
		UK, UK, 1998. Springer-Verlag.

		\bibitem{CV}
		Robert Carr and Santosh Vempala.
		\newblock On the held-karp relaxation for the asymmetric and symmetric
		traveling salesman problems.
		\newblock {\em Mathematical Programming}, 100(3):569--587, Jul 2004.

		\bibitem{gerard}
		G{\'e}rard Cornu{\'e}jols, Jean Fonlupt, and Denis Naddef.
		\newblock The traveling salesman problem on a graph and some related integer
		polyhedra.
		\newblock {\em Mathematical Programming}, 33(1):1--27, Sep 1985.

		\bibitem{fp1}
		Matteo Fischetti, Fred Glover, and Andrea Lodi.
		\newblock The feasibility pump.
		\newblock {\em Mathematical Programming}, 104(1):91--104, Sep 2005.

		\bibitem{fp2}
		Matteo Fischetti and Domenico Salvagnin.
		\newblock Feasibility pump 2.0.
		\newblock {\em Mathematical Programming Computation}, 1(2):201--222, Oct 2009.

		\bibitem{GJ79}
		M.R. Garey and D.S. Johnson.
		\newblock {\em Computers and Intractability -- A Guide to the Theory of
			{NP}-Completeness}.
		\newblock Freeman, San Francisco, CA, 1979.

		\bibitem{cons-cara}
		Martin Gr{\"o}tschel, L{\'a}szl{\'o} Lov{\'a}sz, and Alexander Schrijver.
		\newblock {\em Geometric Algorithms and Combinatorial Optimization}, volume~2.
		\newblock Second corrected edition edition, 1993.

		\bibitem{jain}
		Kamal Jain.
		\newblock A factor 2 approximation algorithm for the generalized steiner
		network problem.
		\newblock In {\em Proceedings of the 39th Annual Symposium on Foundations of
			Computer Science}, FOCS '98, pages 448--, Washington, DC, USA, 1998. IEEE
		Computer Society.

		\bibitem{randomizedrounding}
		Prabhakar Raghavan and Clark~D. Tompson.
		\newblock Randomized rounding: A technique for provably good algorithms and
		algorithmic proofs.
		\newblock {\em Combinatorica}, 7(4):365--374, Dec 1987.

		\bibitem{schrijver}
		A.~Schrijver.
		\newblock {\em Combinatorial Optimization - Polyhedra and Efficiency}.
		\newblock Springer, 2003.

		\bibitem{vazirani}
		Vijay~V. Vazirani.
		\newblock {\em Approximation Algorithms}.
		\newblock Springer-Verlag, Berlin, Heidelberg, 2001.

		\bibitem{sw}
		David~P. Williamson and David~B. Shmoys.
		\newblock {\em The Design of Approximation Algorithms}.
		\newblock Cambridge University Press, New York, NY, USA, 1st edition, 2011.

		\bibitem{Wolsey1980}
		Laurence~A. Wolsey.
		\newblock {\em Heuristic analysis, linear programming and branch and bound},
		pages 121--134.
		\newblock Springer Berlin Heidelberg, Berlin, Heidelberg, 1980.
